\documentclass{article}
\usepackage{amsthm, amsmath, pgfplots, enumitem}
\usepackage[margin=0.5in]{geometry}
\begin{document}
    \noindent\textbf{Math 327 Homework 5}\hfill Anchu A. Lee\\
    \noindent\today\\\\
    \textbf{Question 5.2}: Twelve people are given two identical speakers, which they are asked to listen to for differences, if any. 
    Suppose that these people answer simply by guessing. Find the probability that three people claim to have heard a difference between the two speakers.\\\\
        \indent $\binom{\text{\# of people}}{\text{\# of success}} \cdot \text{probability of success}^{\text{(\# of success})} \cdot \text{probability of failure}^{(\text{\# of fail})}$ \\
        \indent $\binom{12}{3}(\frac{1}{2})^{3}(\frac{1}{2})^{9} = \frac{55}{1024} \approx \textbf{0.0537}$
        \\\\
    \textbf{Question 5.4}: In a certain city district, the need for money to buy drugs is stated as the reason for 75\% of all thefts. 
    Find the probability that among the next 5 theft cases reported in this district,
        \begin{enumerate}[label = (\alph*) ]
            \item  exactly 2 resulted from the need for money to buy drugs; \\\\
                \indent $\binom{5}{2}(\frac{3}{4})^{2}(\frac{1}{4})^{3} = \frac{45}{512} \approx \textbf{0.08789}$
            \item  at most 3 resulted from the need for money to buy drugs. \\\\
                \indent $\binom{5}{3}(\frac{3}{4})^{3}(\frac{1}{4})^{2} = \frac{135}{512}$\\
                \indent $\binom{5}{2}(\frac{3}{4})^{2}(\frac{1}{4})^{3} = \frac{45}{512}$\\
                \indent $\binom{5}{1}(\frac{3}{4})^{1}(\frac{1}{4})^{4} = \frac{15}{1024}$\\
                \indent $\binom{5}{0}(\frac{3}{4})^{0}(\frac{1}{4})^{5} = \frac{1}{1024}$\\
                \indent $\frac{135}{512} + \frac{45}{512} + \frac{15}{1024} + \frac{1}{1024} = \frac{47}{128} \approx \textbf{0.367}$
        \end{enumerate}
    \textbf{Question 5.6}: According to a survey by the Administrative
    Management Society, one-half of U.S. companies give
    employees 4 weeks of vacation after they have been
    with the company for 15 years. Find the probability 
    that among 6 companies surveyed at random, the
    number that give employees 4 weeks of vacation after
    15 years of employment is
        \begin{enumerate}[label = (\alph*) ]
            \item anywhere from 2 to 5;\\\\
                \indent $\binom{6}{2}(\frac{1}{2})^{2}(\frac{1}{2})^{4} + \binom{6}{3}(\frac{1}{2})^{3}(\frac{1}{2})^{3} + \binom{6}{4}(\frac{1}{2})^{4}(\frac{1}{2})^{2} + \binom{6}{5}(\frac{1}{2})^{5}(\frac{1}{2})^{1}$\\
                \indent $\frac{15}{64} + \frac{20}{64} + \frac{15}{64} + \frac{6}{64} = \frac{56}{64} \approx \textbf{0.875}$
            \item fewer than 3.\\\\
                \indent $\binom{6}{2}(\frac{1}{2})^{2}(\frac{1}{2})^{4} + \binom{6}{1}(\frac{1}{2})^{1}(\frac{1}{2})^{5} + \binom{6}{0}(\frac{1}{2})^{0}(\frac{1}{2})^{6}$\\
                \indent $\frac{15}{64} + \frac{6}{64} + \frac{1}{64} = \frac{22}{64} \approx \textbf{0.34375}$
        \end{enumerate}
    \textbf{Question 5.14}: The percentage of wins for the Chicago Bulls
    basketball team going into the playoffs for the 1996–97
    season was 87.7. Round the 87.7 to 90 in order to use
    Table A.1.
        \begin{enumerate}[label = (\alph*) ]
            \item What is the probability that the Bulls sweep (4-0)
            the initial best-of-7 playoff series?\\\\
                \indent $\binom{4}{4}(0.90)^{4}(0.10)^{0} \approx \textbf{0.65}$
            \item What is the probability that the Bulls win the initial 
            best-of-7 playoff series?\\\\
                \indent $\binom{7}{4}(0.90)^{4}(0.10)^{3} + \binom{7}{5}(0.90)^{5}(0.10)^{2} + \binom{7}{6}(0.90)^{6}(0.10)^{1} + \binom{7}{7}(0.90)^{7}(0.10)^{0} \approx \textbf{0.997}$
            \item What very important assumption is made in answering 
            parts (a) and (b)?\\\\
                \indent The probability that the Bulls win any game is always 90\%.
        \end{enumerate}
    \textbf{Question 5.16}: Suppose that airplane engines operate independently 
    and fail with probability equal to 0.4. Assuming
    that a plane makes a safe flight if at least one-half of its
    engines run, determine whether a 4-engine plane or a 2-engine 
    plane has the higher probability for a successful
    flight.\\\\
        \indent 4-engine plane:
        \indent $\binom{4}{2}(0.60)^{2}(0.40)^{2} + \binom{4}{3}(0.60)^{3}(0.40)^{1} + \binom{4}{4}(0.60)^{4}(0.40)^{0} \approx 0.8208$\\
        \indent 2-engine plane:
        \indent $\binom{2}{1}(0.60)^{1}(0.40)^{1} + \binom{2}{2}(0.60)^{2}(0.40)^{0} \approx 0.84$\\
        \indent 2-engine plane has higher chance for a successful flight.\\\\
    \textbf{Question 5.20}: According to USA Today (March 18, 1997), of 4
    million workers in the general workforce, 5.8\% tested
    positive for drugs. Of those testing positive, 22.5\%
    were cocaine users and 54.4\% marijuana users.
        \begin{enumerate}[label = (\alph*)]
            \item What is the probability that of 10 workers testing
            positive, 2 are cocaine users, 5 are marijuana users,
            and 3 are users of other drugs?\\\\
                \indent $\binom{10}{2,5,3}(0.225)^{2}(0.544)^{5}(0.231)^{3} = \frac{10!}{2!5!3!}(0.225)^{2}(0.544)^{5}(0.231)^{3} \approx \textbf{0.0749}$
            \item What is the probability that of 10 workers testing
            positive, all are marijuana users?\\\\
                \indent $\binom{10}{0,10,0}(0.225)^{0}(0.544)^{10}(0.231)^{0} = \frac{10!}{0!10!0!}(0.225)^{0}(0.544)^{10}(0.231)^{0} \approx \textbf{0.00227}$
            \item What is the probability that of 10 workers testing
            positive, none is a cocaine user?\\\\
                \indent $\binom{10}{0,10}(0.225)^{0}(0.775)^{10} = \frac{10!}{0!10!}(0.225)^{0}(0.775)^{10} \approx \textbf{0.0782}$
        \end{enumerate}
    \textbf{Question 5.28}: A manufacturer knows that on average 20\% of
    the electric toasters produced require repairs within 1
    year after they are sold. When 20 toasters are randomly 
    selected, find appropriate numbers x and y such
    that
        \begin{enumerate}[label = (\alph*)]
            \item the probability that at least x of them will require repairs is less than 0.5;\\\\
                \indent $n = 20$, $p = 0.20$, $P(X\geq x)\leq 0.5$ and $P(X<x)>0.5$ gives $x=3$
            \item  the probability that at least y of them will not require repairs is greater than 0.8.\\\\
                \indent $p=0.80$, $P(Y\geq y)\geq 0.8$ and $P(Y<y)<0.2)$ gives $y=15$
        \end{enumerate}
    \textbf{Question 5.30}: To avoid detection at customs, a traveler places
    6 narcotic tablets in a bottle containing 9 vitamin
    tablets that are similar in appearance. If the customs
    official selects 3 of the tablets at random for analysis,
    what is the probability that the traveler will be arrested
    for illegal possession of narcotics?\\\\
        \indent $n=3$, $N = 15$, $k = 6$, $x=0$\\
        \indent $1 - \frac{\binom{6}{0}\cdot \binom{9}{3}}{\binom{15}{3}} = \frac{53}{65} $\\\\
    \textbf{Question 5.32}: From a lot of 10 missiles, 4 are selected at random
    and fired. If the lot contains 3 defective missiles
    that will not fire, what is the probability that
        \begin{enumerate}[label = (\alph*)]
            \item all 4 will fire?\\
                \indent $x=4$, $N=10$, $n=4$, $k=7$\\
                \indent $\frac{\binom{7}{4}\binom{3}{0}}{\binom{10}{4}} = \frac{1}{6}$
            \item at most 2 will not fire?\\
                \indent $k = 3$\\
                \indent $\sum_{x=0}^{2}\frac{\binom{3}{x}\binom{7}{4-x}}{\binom{10}{4}} = \frac{29}{30}$
        \end{enumerate}
    \textbf{Question 5.38}: Among 150 IRS employees in a large city, only
    30 are women. If 10 of the employees are chosen at
    random to provide free tax assistance for the residents
    of this city, use the binomial approximation to the hypergeometric 
    distribution to find the probability that
    at least 3 women are selected.\\\\
        \indent $p = \frac{30}{150} = 0.2$\\
        \indent $1 - \sum_{x=0}^{2}\binom{10}{x}(0.2)^{x}(0.8)^{10-x} \approx \textbf{0.322}$\\\\
    \textbf{Question 5.44}: An urn contains 3 green balls, 2 blue balls, and
    4 red balls. In a random sample of 5 balls, find the
    probability that both blue balls and at least 1 red ball
    are selected.\\\\
        \indent $\frac{\binom{2}{2}\binom{4}{1}\binom{3}{2}}{\binom{9}{5}} + \frac{\binom{2}{2}\binom{4}{2}\binom{3}{1}}{\binom{9}{5}} + \frac{\binom{2}{2}\binom{4}{3}\binom{3}{0}}{\binom{9}{5}} = \frac{17}{63}$\\\\
    \textbf{Question 5.50}: Find the probability that a person flipping a coin
    gets
        \begin{enumerate}[label = (\alph*)]
            \item the third head on the seventh flip;\\
                \indent $\binom{6}{2}(\frac{1}{2})^7 \approx 0.117$ 
            \item the first head on the fourth flip.\\
                \indent $(\frac{1}{2})(\frac{1}{2})^3 = \frac{1}{16}$
        \end{enumerate}
    \textbf{Question 5.54}: According to a study published by a group of
    University of Massachusetts sociologists, about two-thirds 
    of the 20 million persons in this country who
    take Valium are women. Assuming this figure to be a
    valid estimate, find the probability that on a given day
    the fifth prescription written by a doctor for Valium is
        \begin{enumerate}[label = (\alph*)]
            \item the first prescribing Valium for a woman;\\
                \indent Geometric = $g(5;2/3) = (\frac{2}{3})(\frac{1}{3})^4 = \frac{2}{243}$
            \item the third prescribing Valium for a woman.\\
                \indent Negative Binomial = $b^*(5;3,2/3) = \binom{4}{2}(\frac{2}{3})^3(\frac{1}{3})^2 = \frac{16}{81}$
        \end{enumerate}
    \textbf{Question 5.56}: On average, 3 traffic accidents per month occur
    at a certain intersection. What is the probability that
    in any given month at this intersection
        \begin{enumerate}[label = (\alph*)]
            \item exactly 5 accidents will occur?\\
                $p(5;3) = \sum_{x=0}^{5}p(x;3)-\sum_{x=0}^{4}p(x;3)\approx \textbf{0.1008}$
            \item fewer than 3 accidents will occur?\\
                $\sum_{x=0}^{2}p(x;3) \approx \textbf{0.4232}$
            \item at least 2 accidents will occur?\\
                $1-\sum_{x=0}^{1}p(x;2) \approx 1-0.1991 = \textbf{0.8009}$
        \end{enumerate}
    \textbf{Question 5.60}: The average number of field mice per acre in
    a 5-acre wheat field is estimated to be 12. Find the
    probability that fewer than 7 field mice are found
        \begin{enumerate}[label = (\alph*)]
            \item on a given acre;\\
            $\mu = 12$, $r = 6$, $\sum_{x=0}^{6}p(x;12) \approx \textbf{0.0458}$
            \item on 2 of the next 3 acres inspected.\\
            $x = 2$, $n = 3$, $p = 0.0458$\\
            $\binom{3}{2}(0.0458)^2(0.9542)^1 \approx \textbf{0.0060}$
        \end{enumerate}
    \textbf{Question 5.62}: The probability that a student at a local high
    school fails the screening test for scoliosis (curvature
    of the spine) is known to be 0.004. Of the next 1875
    students at the school who are screened for scoliosis, find the probability that
        \begin{enumerate}[label = (\alph*)]
            \item fewer than 5 fail the test;
            \item 8, 9 , or 10 fail the test.
        \end{enumerate}
    \textbf{Question 5.70}: A company purchases large lots of a certain kind
    of electronic device. A method is used that rejects a
    lot if 2 or more defective units are found in a random
    sample of 100 units.
        \begin{enumerate}[label = (\alph*)]
            \item What is the mean number of defective units found
            in a sample of 100 units if the lot is 1\% defective?
            \item What is the variance?
        \end{enumerate}
    \textbf{Question 5.72}:  Potholes on a highway can be a serious problem,
    and are in constant need of repair. With a particular
    type of terrain and make of concrete, past experience
    suggests that there are, on the average, 2 potholes per
    mile after a certain amount of usage. It is assumed
    that the Poisson process applies to the random variable 
    “number of potholes.”
        \begin{enumerate}[label = (\alph*)]
            \item What is the probability that no more than one pothole 
            will appear in a section of 1 mile?
            \item What is the probability that no more than 4 potholes 
            will occur in a given section of 5 miles?
        \end{enumerate}
    \textbf{Question 5.76}: The refusal rate for telephone polls is known to
    be approximately 20\%. A newspaper report indicates
    that 50 people were interviewed before the first refusal.
        \begin{enumerate}[label = (\alph*)]
            \item Comment on the validity of the report. Use a probability 
            in your argument.
            \item What is the expected number of people interviewed
            before a refusal?
        \end{enumerate}
    \textbf{Question 5.78}: An automatic welding machine is being considered
    for use in a production process. It will be considered 
    for purchase if it is successful on 99\% of its welds. 
    Otherwise, it will not be considered efficient.
    A test is to be conducted with a prototype that is to
    perform 100 welds. The machine will be accepted for
    manufacture if it misses no more than 3 welds.
        \begin{enumerate}[label = (\alph*)]
            \item What is the probability that a good machine will
            be rejected?
            \item What is the probability that an inefficient machine
            with 95\% welding success will be accepted?
        \end{enumerate}
    \textbf{Question 5.94}: A production process produces electronic component 
    parts. It is presumed that the probability of a
    defective part is 0.01. During a test of this presumption, 
    500 parts are sampled randomly and 15 defectives
    are observed.
        \begin{enumerate}[label = (\alph*)]
            \item What is your response to the presumption that the
            process is 1\% defective? Be sure that a computed
            probability accompanies your comment.
            \item Under the presumption of a 1\% defective process,
            what is the probability that only 3 parts will be
            found defective?
            \item Do parts (a) and (b) again using the Poisson approximation.
        \end{enumerate}
\end{document}