\documentclass[9pt]{article}
\usepackage{amsthm, amsmath, extsizes, multicol, enumitem}
\usepackage[margin=0.25in]{geometry}
\usepackage[normalem]{ulem}
\begin{document}
\setlength\multicolsep{0pt}
\noindent\uline{\textbf{Chapter 1}}\newline
\uline{Finite Automata} $(Q - $states, $\Sigma - $alphabet, $ \delta - $transitions,
$q_0 - $start, $F\subset Q - $accept$)$. Language is \textbf{regular} if a finite 
automaton recognizes it. Two machines are equivalent if they recognize the same
language.
\begin{itemize}[noitemsep, topsep=0pt]
    \item[-]\uline{Derterministic (DFA)} Restrict to one transition for each unique 
    symbol.
    \item[-]\uline{Nondeterministic (NFA)} Every NFA has an equivalent DFA and any 
    DFA is a valid NFA. Therefore a language is \textbf{regular} if and only if some 
    NFA recognizes it. 
    \item[-]\uline{DFA to NFA} Start at start state(s). Follow and write next possible 
    states per symbol. Create new row for resulting states. Repeat until no new states.
    Should be 1 more state than the NFA.
    \item[-]\uline{Generalized nondeterministic finite automaton (GNFA)} Only one start
    and reject state. Transitions are regular expressions. Used to convert DFA to a RE.
    \item[-]\uline{DFA to DE} Add new start state and accept state. Transition start 
    to old start and from old accept to new accept. Identify destination states from 
    the state that will be removed. Identify all paths destination states have that go
    through the state that will be removed. Write new transitions excluding the removed
    state. Repeat.
\end{itemize}
\uline{Regular Languages} are closed under \textbf{union, intersection, complement, 
concatenation, star (*)}. All finite languages are Regular Languages. \newline
\uline{Power Set} is the set of all subsets of a language. Size of $P(A) = 2^{|A|}$. 
\newline
\uline{Regular Expression}. R is a RE if it is (1) a character in the alphabet 
associated with R. (2) the empty string. (3) the empty language. (4) two regular 
languages under union. (5) two regular languages under concatenation. (6) a regular 
language under star. \textbf{Order of Operations} is parenthesis, star, concatenation,
union. A language described by a RE is \textbf{regular}.\newline
\uline{Pumping Lemma for RL} A string of length at least pumping-length can be broken
up into $xyz$ such that (1) $xy^iz$ is in the language for any $i\geq 0$. (2) $|y|>0$
(3) $|xy| \leq p$.\newline
\uline{Finite Automata Theorems} For a finite automata $M$ with $n$ states (1) $L(M)$ 
is non-empty if and only if $M$ accepts a string of length less than $n$ (2) $L(M)$ is 
infinite if and only if $M$ accepts a string of length $i$ where $n\leq i < 2n$. It is
possible to create a FA that can determine if two FA are equivalent and taking a 
finite amount of time if they are equivalent.\newline
\noindent\uline{\textbf{Chapter 2}}\newline
\uline{Context-free Grammar} ($V-$variables (states), $\Sigma-$terminals (symbols), 
$R-$rules (transitions), $S-$start). Parse-trees show the path the CFG takes to output
the string. Any language made by a CFG is a \textbf{context-free} language. A CFG is
\textbf{ambiguous} if there is more than one way to generate a string (two parse trees). 
A CFL is \textbf{inherently ambiguous} if all grammars for the language are ambiguous. 
\textbf{Leftmost} deviation means the leftmost remaining variable is the one replaced; 
same for rightmost.\newline
\uline{Context-free Languages} are closed under \textbf{union, concatenation, star (*)}. 
All Regular languages are context-free.\newline
\uline{Chomsky Normal Form} if every rule is of the form $A\rightarrow BC$ or 
$A\rightarrow a$. The start variable can have a $\epsilon$. (1) Add new start variable 
with rule to old start variable. (2) Eliminate all $\epsilon$ rules. (3) Eliminate all
unit rules. (3) Convert remaining to proper form by moving stuff around. Any CFL can be 
generated by a CFG in Chomsky normal form.\newline
\uline{Pushdown Automata (PDA)} Same setup as a FA, except the inclusion of a stack
and the transitions that can pop or push something on the stack. A language is 
\textbf{context-free} if and only if some PDA recognizes it. Every regular language is
context-free.\newline
\uline{Pumping Lemma for CFL} If L is a CFL, then there is a pumping-length where if
a string in L is at least pumping-length then the string can be broken up into $uvxyz$
where (1) $uv^ixy^iz \in L$ for all $i\geq 0$. (2) $|xy|>0$ (3) $|vxy|\geq p$\newline
\uline{\textbf{Examples}}\newline
\uline{Prove $\{0^n1^m0^n \mid m,n \geq 0\}$ is not regular.} Assume this language 
($A$) is regular, so then there must exist a variable $p$, the pumping length. Choose 
$w = 0^p10^p$ as the test word. $|w|>p$ and $w\in A$. As $|xy|\leq p$, $x$ and $y$ must 
be composed of only zeros. Additionally, as $|y|>0$, $y$ would then have to equal $0^k$ 
for some $k>0$. For $xy^iz$, choose $i=0$ and the resulting word should still be in $A$. 
However $xy^0z=xz = 0^{p-k}10^p$. This resulting word is not in $A$ therefore our 
assumption was incorrect.\newline
\uline{Prove $\{a^nb^m \mid m \leq n^2\}$ is not context-free.} Choose $S = a^{p+1}
b^{p^2+1}$ There are then three cases for $vxy$. (1) $a^{p+1}$, (2) $a^pb^{p^2}$, (3) 
$b^{p^2+1}$. We pump down on case 1 and 2, and pump up for case 3. For case 1, the 
number of b's is greater than the number of a's squared ($a^{p+1-1}b^{p^2+1}$). For 
case 2, the number of a's and b's become equal ($ab$), which is not what the language 
wants. For case 3, the number of a's squared will be greater than the number of b's.
($a^{p+1}b^{p^2+1+1}$). With all options exhausted, the language cannot be context-free.
\newline
\uline{Convert the following CFG to Chomsky normal form.} (S is already new start state)
\newline
\begin{minipage}[t]{.3\textwidth}
$S\rightarrow aAA\mid aBC \mid abc$\newline
$A\rightarrow AA\mid Aa\mid ab$\newline
$B\rightarrow aaBC\mid BC$\newline
$C\rightarrow a\mid bc$
\end{minipage}% <---------------- Note the use of "%"
\begin{minipage}[t]{.3\textwidth}
$S\rightarrow DAA\mid DBC \mid DEF$\newline
$A\rightarrow AA\mid AD\mid DE$\newline
$B\rightarrow DDBC\mid BC$\newline
$C\rightarrow a\mid EF$\newline
$D\rightarrow a$\newline
$E\rightarrow b$\newline
$F\rightarrow c$
\end{minipage}%
\begin{minipage}[t]{.3\textwidth}
$S\rightarrow DI\mid DH \mid DJ$\newline
$A\rightarrow AA\mid AD\mid DE$\newline
$B\rightarrow GH\mid BC$\newline
$C\rightarrow a\mid EF$\newline
$D\rightarrow a$\newline
$E\rightarrow b$\newline
$F\rightarrow c$\newline
$G\rightarrow DD$\newline
$H\rightarrow BC$\newline
$I\rightarrow AA$\newline
$J\rightarrow EF$
\end{minipage}\newline
\uline{Removing $\epsilon$ rules from CFGs}\newline
\begin{minipage}[t]{.20\textwidth}
$A\rightarrow B\mid C$\newline
$B\rightarrow aCa\mid \epsilon$\newline
$C\rightarrow bAb\mid \epsilon$
\end{minipage}%
\begin{minipage}[t]{.20\textwidth}
$S\rightarrow A$\newline
$A\rightarrow B\mid C$\newline
$B\rightarrow aCa\mid \epsilon$\newline
$C\rightarrow bAb\mid \epsilon$
\end{minipage}%
\begin{minipage}[t]{.20\textwidth}
$S\rightarrow A \mid \epsilon$\newline
$A\rightarrow B\mid C$\newline
$B\rightarrow aCa\mid aa$\newline
$C\rightarrow bAb\mid bb$
\end{minipage}%
\begin{minipage}[t]{.20\textwidth}
$S\rightarrow A \mid \epsilon$\newline
$A\rightarrow B\mid C$\newline
$B\rightarrow DCD\mid DD$\newline
$C\rightarrow EAE\mid EE$\newline
$D\rightarrow a$\newline
$E\rightarrow b$
\end{minipage}%
\begin{minipage}[t]{.20\textwidth}
$S\rightarrow A \mid \epsilon$\newline
$A\rightarrow B\mid C$\newline
$B\rightarrow DF\mid DD$\newline
$C\rightarrow GE\mid EE$\newline
$D\rightarrow a$\newline
$E\rightarrow b$\newline
$F\rightarrow CD$\newline
$G\rightarrow EA$
\end{minipage}
\end{document}