\documentclass{article}
\usepackage{amsthm, amsmath, graphicx, enumitem, tikz-qtree}
\usepackage[margin=0.5in]{geometry}
\begin{document}
    \noindent\textbf{CS 373 Homework 9}\hfill Anchu A. Lee\\
    \noindent\today\\
    \begin{enumerate}
        \item Let Some$_{DFA} = $\{ $\langle A \rangle \mid $ $A$ is a DFA and $L(A)$ is 
        not empty and $L(A)$ is not equal to $\Sigma^*$ \}. Show that 
        Some$_{DFA}$ is decidable.
        \begin{description}
            \item Construct a Turing machine $M$ to decide the Some$_{DFA}$ problem.
            \item On input $d$ that is a DFA:
            \begin{enumerate}[label=\arabic*.]
                \item Run $\langle d\rangle$ on a Turing machine $T$ that decides E$_{DFA}$, 
                if $T$ rejects then continue, if $T$ accepts, then reject.
                \item Construct a DFA d$^{C}$ that is the compliment of $d$.
                \item Run $\langle$d$^{C}\rangle$ on a turing machine $T$, if $T$ rejects
                then accept $d$, if $T$ accepts then reject $d$.
            \end{enumerate}
            \item If $d$ is not a DFA, then $M$ rejects. If $L(d)$ is empty, then $M$ rejects. 
            If the compliment of $d$ is empty, meaning  $L(d)=\Sigma^*$, then $M$ rejects. 
            Otherwise $M$ accepts. All conditions are handled in $M$ so $M=$ Some$_{DFA}$.
        \end{description}
        
        \item Let Alot$_{RE} = $\{ $\langle A \rangle \mid $ $A$ is a regular expression 
        and $L(A)$ is infinite \}. Show that Alot$_{RE}$ is decidable.
        \begin{description}
            \item Construct a Turing machine $M$ to decide the Alot$_{RE}$ problem.
            \item On input $r$ that is a RE:
            \begin{enumerate}[label=\arabic*.]
                \item Construct a DFA $A$ that is equivalent to $r$.
                \item For $s$ that is the number of states in $A$, construct DFA $B$ that accepts
                all strings over the alphabet in $A$ that are at least length $s$.
                \item Construct a DFA $C$ so that $L(C) = L(A) \cap L(B)$.
                \item Run $\langle C \rangle$ on a turing machine $T$ that decides E$_{DFA}$.
                \item If $T$ accepts then reject $r$, if $T$ rejects then accept $r$.
            \end{enumerate}
            \item In order for a DFA to accept an infinite language, it must contain a loop. If
            a DFA contains a string with a length greater than the number of states, then it contains
            a loop and therefore accepts an infinite language. The Turing machine $M$ checks if a RE
            accepts an infinite language by intersecting the language accepted by $r$ to the language
            of strings with length greater than the number of states of the DFA for $r$. $M$ accepts if
            the intersection is non-empty and rejects otherwise. Therefore $M=$ Alot$_{RE}$.
        \end{description}
        \item Let $Complimentary_{RE,DFA} = $\{ $\langle A, B \rangle \mid $ $A$ is a 
        regular expression and $B$ is a DFA such that $L(A) \cup L(B) = \Sigma^*$ and 
        $L(A) \cap L(B) = $\O \}. Show that $Complimentary_{RE,DFA}$ is decidable.

        \item Let $ALL_{DFA} = $\{ $\langle A \rangle \mid A$ is a DFA and $L(A) = 
        \Sigma^* $\}. Show that $ALL_{DFA}$ is decidable.

        \item Let $N_{\varepsilon CFG} = $\{ $\langle G \rangle \mid G$ is a CFG and $G$ 
        does not generate the empty string \}. Show that $N_{\varepsilon CFG}$ is 
        decidable.

        \item Let $X$ be the set \{1, 2, 3, 4, 5\} and $Y$ be the set \{6, 7, 8, 9, 10\}. 
        We describe the functions $f : X\rightarrow Y$ and $g : X \rightarrow Y$ in the 
        following tables. Answer each part and give a reason for each negative answer.
        \begin{center}
            \begin{tabular}{c|c}
                $n$ & $f(n)$\\
                \hline
                1 & 6\\
                2 & 7\\
                3 & 6\\
                4 & 7\\
                5 & 6
            \end{tabular}
            \quad
            \begin{tabular}{c | c}
                $n$ & $g(n)$\\
                \hline
                1 & 10\\
                2 & 9\\
                3 & 8\\
                4 & 7\\
                5 & 6
            \end{tabular}
        \end{center}
        \begin{enumerate}
            \item Is $f$ onto?
            \item Is $f$ a correspondence?
            \item Is $g$ onto?
            \item Is $g$ a correspondence?
        \end{enumerate}

        \item Let $U = $\{ $\langle A, B, C \rangle \mid A, B, C$ are DFA's and $|L(A)| = 
        |L(B)| + |L(C)|$ \}. Show that $U$ is decidable.

        \item Let $A = $\{ $\langle R \rangle \mid R$ is a regular expression describing a 
        language containing at least one string $w$ that has 111 as a substring (i.e., 
        $w = x111y$ for some $x$ and $y$)\}. Show that $A$ is decidable.
        
        \item Let $E_{PDA} = $\{ $\langle P \rangle \mid P$ is a pushdown automata and 
        $L(P)$ is empty \}. Show $E_{PDA}$ is decidable.

        \item A \textbf{\textit{useless state}} in a pushdown automaton is never entered 
        on any input string. Consider the problem of determining whether a pushdown 
        automaton has any useless states. Formulate this problem as a language and show 
        that it is decidable.
    \end{enumerate}
\end{document}