\documentclass[12pt]{article}
\usepackage{enumitem, datetime, comment}
\usepackage[margin=1in]{geometry}
\newdateformat{monthyear}{\monthname[\THEMONTH], \THEYEAR}
\pagenumbering{gobble}
\excludecomment{hiringmgr}
\newcommand{\firstname}{Anchu}
\newcommand{\lastname}{Lee}
\newcommand{\middlename}{A}
\newcommand{\addressA}{189 West End Ave.}
\newcommand{\addressB}{Binghamton, NY 13905}
\newcommand{\email}{alee845@binghamton.edu}
\newcommand{\phonenumber}{(607) 297-8847}
\newcommand{\university}{Binghamton University}
\newcommand{\gpa}{3.48}

\newcommand{\applyingposition}{Summer 2018 Cyber Security Internship}
\newcommand{\companyname}{BAE Systems}
\newcommand{\companyaddressA}{8201 Greensboro Drive Suite 1200}
\newcommand{\companyaddressB}{McLean, VA 22102}
\newcommand{\companyhiringmanager}{[Hiring Manager]}
\newcommand{\companyhiringmanageremail}{[Hiring Manager Email]}

\newcommand{\name}{\firstname{ }\middlename{. }\lastname}

\begin{document}
    \begin{center}
        {\Large\textbf{\name}}\\\addressA\\\addressB\\\email\\\phonenumber\\
    \end{center}
    \monthyear\today\\
\begin{hiringmgr}
    \companyhiringmanager\\
    \companyhiringmanageremail\\\newline
\end{hiringmgr}
    \companyname\\
    \companyaddressA\\
    \companyaddressB\\\newline
    Hello,\newline
    \indent My name is \firstname{ }\lastname{ }and I am grateful for the opportunity to
    apply for the \applyingposition{ }at \companyname. After reviewing your job listing,
    I believe that I have the necessary skills and traits you are looking for.\newline
    \indent I am currently a college student at \university{ }studying Computer Science with a 
    GPA of \gpa. Since the beginning of my academic career, I have on the lookout for opportunities 
    to gain experience and improve myself. Thanks to my enthusiasm, I was one of the few freshman 
    in history to be voted into the board of officers for the Taiwanese American Student Coalition. 
    I have also applied for various course assistant and tutoring positions within the computer 
    science department. This semester I am the course assistant for a senior level computer 
    science course.\newline
    \indent I have always been interested in computer security, especially how exploits
    are found and how to prevent them. For many of my projects, I always take extra care with
    security. For one hackathon project, I made sure my JavaScript web-app had proper input 
    sanitation, SSL encryption and authentication even with a deadline of only 24 hours. In the
    spring semester, I will be taking Computer Networks and Computer Security so I will have 
    a even stronger foundation of computer security by summertime.\newline
    \indent I hope that after you review my resume, you will agree that I am a qualified and
    enthusiastic candidate. I will be more than happy to elaborate on any of my specific skills or 
    experiences in the future. \newline
    \indent Thank you for considering me as a candidate for this position, I look forward to hearing
    from you soon.
\end{document}